Predicting Fatalities in Toronto Car Crashes: Analyzing the Impact of Time, Vehicle Type, and Other Collision Determinants

### 2024-12-04 paper/paper.qmd
updated model card

- **Hour and Motorcycle**:
  - `hour1 × motorcycle`: 31.900, significant interaction in early morning hours, suggesting motorcycle accidents are more likely during certain hours.
  - Other significant hours for motorcycle collisions are `hour6 × motorcycle` (51.053) and `hour9 × motorcycle` (-66.051).
- **Hour and Pedestrian**:
  - `hour1 × pedestrian`: 15.095, significant pedestrian accidents in the early morning hours.
  - Other significant hours include `hour2 × pedestrian` (29.594) and `hour5 × pedestrian` (23.943), highlighting peak pedestrian accident hours.

>>>>

- **Hour and Motorcycle**:
  - `hour1 × motorcycle`: 33.237, significant interaction in early morning hours, suggesting motorcycle accidents are more likely during certain hours.
  - Other significant hours for motorcycle collisions are `hour12 × motorcycle` (54.822) and `hour23 × motorcycle` (37.984).
- **Hour and Pedestrian**:
  - `hour1 × pedestrian`: 15.758, significant pedestrian accidents in the early morning hours.
  - Other significant hours include `hour2 × pedestrian` (29.368) and `hour5 × pedestrian` (22.835), highlighting peak pedestrian accident hours.
